\protect Connecting every bit of knowledge: \\ The structure of Wikipedia's First Link Network

### 2016-05-02 writeup/2016-04wikipedia-network/correspondence/2016-05-02compsci-highlights.tex
compsci submission

Mark Ibrahim is an applied mathematician who's interested in exploring how humans structure and interact with information. Before studying applied mathematics, Mark received a B.A. from Hamilton College where he also studied philosophy, economics, English, and French. Mark has experience in industry assessing market risk using portfolio trading data. He is currently building a project to search videos with speech and a second project serving a network search engine powered by Wikipedia.

Chris Danforth is the Flint Professor of Mathematical, Natural, and Technical Sciences at the University of Vermont. He co-directs the Computational Story Lab, a group of applied mathematicians at the undergraduate, masters, PhD, and postdoctoral level working on large-scale, system problems in many fields including sociology, nonlinear dynamics, networks, ecology, and physics. His research has been covered by the New York Times, Science Magazine, and the BBC among others. Descriptions of his projects are available at his website: http://uvm.edu/∼cdanfort

Peter Sheridan Dodds is a Professor at the University of Vermont (UVM) working on system-level problems in many fields, ranging from sociology to physics. He is Director of UVM's Complex Systems Center, co-Director of UVM's Computational Story Lab, a visiting faculty fellow at the Vermont Advanced Computing Core, and is appointed to the Department of Mathematics and Statistics. He maintains general research and teaching interests in complex systems and networks with a current focus on sociotechnical and psychological phenomena including collective emotional states, contagion, language, and stories. His methods encompass large-scale data collection and analysis, large-scale sociotechnical experiments, and the formulation, analysis, and simulation of theoretical models. Dodds's training is in theoretical physics, mathematics, and electrical engineering with extensive formal postdoctoral and research experience in the social sciences. Dodds's foundational funding was an  NSF CAREER grant awarded by the Social and Economic Sciences Directorate.

>>>>

Our major contributions and findings are as follows:

\textbf{1.}
We connect all 4.7 million Wikipedia articles in a directed network via the first link.
The network reflects how the many inventions, places, figures, objects, and events are related and organized.

\textbf{2.}
We develop a novel algorithm to map the structure of a directed network as a flow. Our measures quantify: \\
\mbox{}\ \textbf{a.}
where references accumulate\\
\mbox{}\ \textbf{b.}
groups of path-connected nodes\\
\mbox{}\ \textbf{c.}
the influence each node exerts in shaping the network.

\textbf{3.}
We identify a gravitation of references on Wikipedia from  specific to general, which culminates disproportionately around only a few fundamental notions.

Our findings form the basis for a new network-based topic search engine with applications in natural language processing and cognitive psychology.

### 2016-05-02 writeup/2016-04wikipedia-network/correspondence/2016-05-02compsci.tex
compsci submission

@@

@@

>>>>

\raisebox{-4pt}{
%% \includegraphics[width=0.4\textwidth]{uvm-towerlogoK.png}
%% \includegraphics[width=0.4\textwidth]{uvm-towerlogo2C.jpg}
\includegraphics[width=0.2\textwidth]{roboctopus.png}
%% \includegraphics[height=68pt]{psd_1.jpg}
}
% \textcolor{DarkSlateBlue}{
{ \small
\begin{tabular}[b]{l}
Prof.\ Peter Sheridan Dodds\\
Director of the Vermont Complex Systems Center\\
Co-Director, Computational Story Lab\\
%% \Letter\
%% Department of Mathematics and Statistics\\
%% University of Vermont\\
210 Colchester Avenue, Burlington, VT, 05401, USA\\
%% \Lightning
%% \Email\
pdodds@uvm.edu
$\bullet$
http://www.uvm.edu/{$\sim$}pdodds
% \Mobilefone
% +1-917-533-8135 % (cell)
% $\bullet$
% \Telefon 
% +1-802-656-3089 % (home)
\end{tabular}
}
% \raisebox{-16pt}{
% \includegraphics[height=68pt]{psd_1.jpg}
% }

@@

To the Editors,

We are very pleased to submit our manuscript for consideration at the Journal of Computational Science:\\
\textbf{``Connecting every bit of knowledge:
The structure of Wikipedia\textquotesingle s First Link Network''.}

@@

We look forward to hearing your decision.

Yours sincerely and on behalf of the manuscript's authors,

\includegraphics[width=0.2\textwidth]{signature}\\
Mark Ibrahim
